Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-08 docs/google-research-awards-latam/main.tex
updated related works (wip)

\vspace{1ex} \textbf{Related Work.}~\Fix{...}~\cite{maddox-2015-acmqueue}

>>>>

\vspace{1ex} \textbf{Related Work.}
~According Maddox \cite{maddox-2015-acmqueue}, is very complex to testing 
distributed system that have multiple components due lack of configurations, 
data-flow between nodes and asynchronous behaviour. (wip)

Fuzzing is a very common technique used in software engineering for
generate code mutations from existing test sample to improve the black-box testing method.
In Yang et al. \cite{yang-2011-finding}, it was designed the 
CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
based on C language to generate invalid entries and found bugs in several C compilers.
Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
that exposes the LangFuzz to generate entries based in code fragments 
(language grammar, sample code, test suite) and the tool Mozilla 
Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
that implements a fuzzer based on JavaScript language to improve the 
testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
\Fix{...}
